---
title: "Social factors DataSchema"
output: html_document
---

# Table of Contents  
1. [Social network subdomain](#social-network-subdomain)  
2. [Social support subdomain](#social-support-subdomain)  
3. [Social participation subdomain](#social-participation-subdomain)  
4. [Major life events subdomain](#major-life-events-subdomain)  
5. [Residential characteristics subdomain](#residential-characteristics-subdomain)

# Social network subdomain

### **Variable label**:   Network size of children      
**Variable name**:   soc_sn_num_children_0    
**Variable description**:  Indicator of the number of living biological, adopted or step children.      
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of children      
**Variable name**:   soc_sn_num_children_1    
**Variable description**:  Indicator of the number of living biological, adopted or step children.          
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of children      
**Variable name**:   soc_sn_num_children_2    
**Variable description**:  Indicator of the number of living biological, adopted or step children.        
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of children      
**Variable name**:   soc_sn_num_children_3    
**Variable description**:  Indicator of the number of living biological, adopted or step children.         
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of children      
**Variable name**:   soc_sn_num_children_4    
**Variable description**:  Indicator of the number of living biological, adopted or step children.         
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of children      
**Variable name**:   soc_sn_num_children_5    
**Variable description**:  Indicator of the number of living biological, adopted or step children.          
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of children      
**Variable name**:   soc_sn_num_children_6    
**Variable description**:  Indicator of the number of living biological, adopted or step children.          
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Ranked network size of children         
**Variable name**:   soc_sn_children_rank_0      
**Variable description**:  Indicator of whether the participant has a low, medium or high network size compromised of children. It is measured by ranking the size of the network which is comprised of any type of child (biological, step, adoptive, foster, in-law son/daughter).  Low rank indicates no children.  Note: cohorts inquire about different types of children due to the particular questionnaire used, therefore a childless respondent in one study would not necessarily be considered childless in another study.  
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |  Low rank of network size comprised of children (childless) 
1 |  Medium rank of network size comprised of children  (1 or 2 children)
2 |  Large rank of network size comprised of children  (more than 2 children) 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Ranked network size of children           
**Variable name**:   soc_sn_children_rank_1      
**Variable description**:  Indicator of whether the participant has a low, medium or high network size compromised of children. It is measured by ranking the size of the network which is comprised of any type of child (biological, step, adoptive, foster, in-law son/daughter).  Low rank indicates no children.  Note: cohorts inquire about different types of children due to the particular questionnaire used, therefore a childless respondent in one study would not necessarily be considered childless in another study.  
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |  Low rank of network size comprised of children (childless) 
1 |  Medium rank of network size comprised of children  (1 or 2 children)
2 |  Large rank of network size comprised of children  (more than 2 children)  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Ranked network size of children           
**Variable name**:   soc_sn_children_rank_2      
**Variable description**:  Indicator of whether the participant has a low, medium or high network size compromised of children. It is measured by ranking the size of the network which is comprised of any type of child (biological, step, adoptive, foster, in-law son/daughter).  Low rank indicates no children.  Note: cohorts inquire about different types of children due to the particular questionnaire used, therefore a childless respondent in one study would not necessarily be considered childless in another study.    
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |  Low rank of network size comprised of children (childless) 
1 |  Medium rank of network size comprised of children  (1 or 2 children)
2 |  Large rank of network size comprised of children  (more than 2 children)  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Ranked network size of children          
**Variable name**:   soc_sn_children_rank_3      
**Variable description**:  Indicator of whether the participant has a low, medium or high network size compromised of children. It is measured by ranking the size of the network which is comprised of any type of child (biological, step, adoptive, foster, in-law son/daughter).  Low rank indicates no children.  Note: cohorts inquire about different types of children due to the particular questionnaire used, therefore a childless respondent in one study would not necessarily be considered childless in another study.  
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |  Low rank of network size comprised of children (childless) 
1 |  Medium rank of network size comprised of children  (1 or 2 children)
2 |  Large rank of network size comprised of children  (more than 2 children)  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Ranked network size of children          
**Variable name**:   soc_sn_children_rank_4      
**Variable description**:  Indicator of whether the participant has a low, medium or high network size compromised of children. It is measured by ranking the size of the network which is comprised of any type of child (biological, step, adoptive, foster, in-law son/daughter).  Low rank indicates no children.  Note: cohorts inquire about different types of children due to the particular questionnaire used, therefore a childless respondent in one study would not necessarily be considered childless in another study.  
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |  Low rank of network size comprised of children (childless) 
1 |  Medium rank of network size comprised of children  (1 or 2 children)
2 |  Large rank of network size comprised of children  (more than 2 children)  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Ranked network size of children          
**Variable name**:   soc_sn_children_rank_5      
**Variable description**:  Indicator of whether the participant has a low, medium or high network size compromised of children. It is measured by ranking the size of the network which is comprised of any type of child (biological, step, adoptive, foster, in-law son/daughter).  Low rank indicates no children.  Note: cohorts inquire about different types of children due to the particular questionnaire used, therefore a childless respondent in one study would not necessarily be considered childless in another study.  
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |  Low rank of network size comprised of children (childless) 
1 |  Medium rank of network size comprised of children  (1 or 2 children)
2 |  Large rank of network size comprised of children  (more than 2 children)  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Ranked network size of children         
**Variable name**:   soc_sn_children_rank_6      
**Variable description**:  Indicator of whether the participant has a low, medium or high network size compromised of children. It is measured by ranking the size of the network which is comprised of any type of child (biological, step, adoptive, foster, in-law son/daughter).  Low rank indicates no children.  Note: cohorts inquire about different types of children due to the particular questionnaire used, therefore a childless respondent in one study would not necessarily be considered childless in another study.  
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |  Low rank of network size comprised of children (childless) 
1 |  Medium rank of network size comprised of children  (1 or 2 children)
2 |  Large rank of network size comprised of children  (more than 2 children)  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Network size of friends    
**Variable name**:   soc_sn_num_friends_0  
**Variable description**:  Indicator of the number of close friends. These are friends which the participant feels they can talk to/reach out to.    
**Value type**:  integer  
**Variable unit**:   
**Category coding**:      

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of friends    
**Variable name**:   soc_sn_num_friends_1    
**Variable description**:  Indicator of the number of close friends. These are friends which the participant feels they can talk to/reach out to.  
**Value type**:  integer  
**Variable unit**:   
**Category coding**:      

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of friends    
**Variable name**:   soc_sn_num_friends_2    
**Variable description**:  Indicator of the number of close friends. These are friends which the participant feels they can talk to/reach out to.    
**Value type**:  integer  
**Variable unit**:   
**Category coding**:      

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of friends    
**Variable name**:   soc_sn_num_friends_3    
**Variable description**:  Indicator of the number of close friends. These are friends which the participant feels they can talk to/reach out to.    
**Value type**:  integer  
**Variable unit**:   
**Category coding**:      

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of friends    
**Variable name**:   soc_sn_num_friends_4    
**Variable description**:  Indicator of the number of close friends. These are friends which the participant feels they can talk to/reach out to.    
**Value type**:  integer  
**Variable unit**:   
**Category coding**:      

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of friends    
**Variable name**:   soc_sn_num_friends_5    
**Variable description**:  Indicator of the number of close friends. These are friends which the participant feels they can talk to/reach out to.      
**Value type**:  integer  
**Variable unit**:   
**Category coding**:      

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Network size of friends    
**Variable name**:   soc_sn_num_friends_6    
**Variable description**:  Indicator of the number of close friends. These are friends which the participant feels they can talk to/reach out to.    
**Value type**:  integer  
**Variable unit**:   
**Category coding**:      

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   In-person contact frequency with friends        
**Variable name**:   soc_sn_freq_friends_inperson_0       
**Variable description**:   Indicator of in-person contact frequency with close friends. This is a different variable than soc_sn_freq_friends, which is an indicator for contact frequency but not necessarily in-person contact.    
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily in-person contact with friends  
2 |  Weekly in-person contact with friends  
3 |  Biweekly in-person contact with friends   
4 |  Monthly in-person contact with friends   
5 |  Never or less than a year in-person contact with friends  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   In-person contact frequency with friends        
**Variable name**:   soc_sn_freq_friends_inperson_1       
**Variable description**:   Indicator of in-person contact frequency with close friends. This is a different variable than soc_sn_freq_friends, which is an indicator for contact frequency but not necessarily in-person contact.    
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily in-person contact with friends  
2 |  Weekly in-person contact with friends  
3 |  Biweekly in-person contact with friends   
4 |  Monthly in-person contact with friends   
5 |  Never or less than a year in-person contact with friends     

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   In-person contact frequency with friends        
**Variable name**:   soc_sn_freq_friends_inperson_2       
**Variable description**:   Indicator of in-person contact frequency with close friends. This is a different variable than soc_sn_freq_friends, which is an indicator for contact frequency but not necessarily in-person contact.    
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily in-person contact with friends  
2 |  Weekly in-person contact with friends  
3 |  Biweekly in-person contact with friends   
4 |  Monthly in-person contact with friends   
5 |  Never or less than a year in-person contact with friends  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   In-person contact frequency with friends       
**Variable name**:   soc_sn_freq_friends_inperson_3       
**Variable description**:   Indicator of in-person contact frequency with close friends. This is a different variable than soc_sn_freq_friends, which is an indicator for contact frequency but not necessarily in-person contact.    
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily in-person contact with friends  
2 |  Weekly in-person contact with friends  
3 |  Biweekly in-person contact with friends   
4 |  Monthly in-person contact with friends   
5 |  Never or less than a year in-person contact with friends       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   In-person contact frequency with friends       
**Variable name**:   soc_sn_freq_friends_inperson_4       
**Variable description**:   Indicator of in-person contact frequency with close friends. This is a different variable than soc_sn_freq_friends, which is an indicator for contact frequency but not necessarily in-person contact.    
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily in-person contact with friends  
2 |  Weekly in-person contact with friends  
3 |  Biweekly in-person contact with friends   
4 |  Monthly in-person contact with friends   
5 |  Never or less than a year in-person contact with friends    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Contact frequency with friends        
**Variable name**:   soc_sn_freq_friends_0       
**Variable description**:   Indicator of contact frequency with close friends.         
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily contact with friends 
2 |  Weekly contact with friends
3 |  Biweekly contact with friends
4 |  Monthly contact with friends
5 |  Never or less than a year contact with friends

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Contact frequency with friends        
**Variable name**:   soc_sn_freq_friends_1       
**Variable description**:   Indicator of contact frequency with close friends.         
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily contact with friends 
2 |  Weekly contact with friends
3 |  Biweekly contact with friends
4 |  Monthly contact with friends
5 |  Never or less than a year contact with friends 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Contact frequency with friends        
**Variable name**:   soc_sn_freq_friends_2       
**Variable description**:   Indicator of contact frequency with close friends.         
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily contact with friends 
2 |  Weekly contact with friends
3 |  Biweekly contact with friends
4 |  Monthly contact with friends
5 |  Never or less than a year contact with friends 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Contact frequency with friends        
**Variable name**:   soc_sn_freq_friends_3       
**Variable description**:   Indicator of contact frequency with close friends.         
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily contact with friends 
2 |  Weekly contact with friends
3 |  Biweekly contact with friends
4 |  Monthly contact with friends
5 |  Never or less than a year contact with friends

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Contact frequency with friends        
**Variable name**:   soc_sn_freq_friends_4       
**Variable description**:   Indicator of contact frequency with close friends.         
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily contact with friends 
2 |  Weekly contact with friends
3 |  Biweekly contact with friends
4 |  Monthly contact with friends
5 |  Never or less than a year contact with friends  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Contact frequency with friends        
**Variable name**:   soc_sn_freq_friends_5       
**Variable description**:   Indicator of contact frequency with close friends.         
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily contact with friends 
2 |  Weekly contact with friends
3 |  Biweekly contact with friends
4 |  Monthly contact with friends
5 |  Never or less than a year contact with friends  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Contact frequency with friends        
**Variable name**:   soc_sn_freq_friends_6       
**Variable description**:   Indicator of contact frequency with close friends.         
**Value type**:  integer  
**Variable unit**:   
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 |  Daily contact with friends 
2 |  Weekly contact with friends
3 |  Biweekly contact with friends
4 |  Monthly contact with friends
5 |  Never or less than a year contact with friends 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Network size of neighbours           
**Variable name**:   soc_sn_num_nbhs_0    
**Variable description**:  Indicator of the number of neighbours that participant knows well enough to be in touch with or visit with.  
**Value type**:  integer    
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | No neighbours 
2 | 1 or 2 neighbours 
3 | 3 to 5 neighbours 
4 | 6 to 10 neighbours 
5 | 11 to 20 neighbours 
6 | More than 20 neighbours   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Network size of neighbours           
**Variable name**:   soc_sn_num_nbhs_1    
**Variable description**:  Indicator of the number of neighbours that participant knows well enough to be in touch with or visit with.  
**Value type**:  integer    
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | No neighbours 
2 | 1 or 2 neighbours 
3 | 3 to 5 neighbours 
4 | 6 to 10 neighbours 
5 | 11 to 20 neighbours 
6 | More than 20 neighbours    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Network size of neighbours           
**Variable name**:   soc_sn_num_nbhs_2    
**Variable description**:  Indicator of the number of neighbours that participant knows well enough to be in touch with or visit with.  
**Value type**:  integer    
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | No neighbours 
2 | 1 or 2 neighbours 
3 | 3 to 5 neighbours 
4 | 6 to 10 neighbours 
5 | 11 to 20 neighbours 
6 | More than 20 neighbours    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Network size of neighbours           
**Variable name**:   soc_sn_num_nbhs_3    
**Variable description**:  Indicator of the number of neighbours that participant knows well enough to be in touch with or visit with.  
**Value type**:  integer    
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | No neighbours 
2 | 1 or 2 neighbours 
3 | 3 to 5 neighbours 
4 | 6 to 10 neighbours 
5 | 11 to 20 neighbours 
6 | More than 20 neighbours    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Network size of neighbours           
**Variable name**:   soc_sn_num_nbhs_4    
**Variable description**:  Indicator of the number of neighbours that participant knows well enough to be in touch with or visit with.  
**Value type**:  integer    
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | No neighbours 
2 | 1 or 2 neighbours 
3 | 3 to 5 neighbours 
4 | 6 to 10 neighbours 
5 | 11 to 20 neighbours 
6 | More than 20 neighbours    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Network size of neighbours           
**Variable name**:   soc_sn_num_nbhs_5    
**Variable description**:  Indicator of the number of neighbours that participant knows well enough to be in touch with or visit with.  
**Value type**:  integer    
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | No neighbours 
2 | 1 or 2 neighbours 
3 | 3 to 5 neighbours 
4 | 6 to 10 neighbours 
5 | 11 to 20 neighbours 
6 | More than 20 neighbours    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Network size of neighbours           
**Variable name**:   soc_sn_num_nbhs_6    
**Variable description**:  Indicator of the number of neighbours that participant knows well enough to be in touch with or visit with.  
**Value type**:  integer    
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | No neighbours 
2 | 1 or 2 neighbours 
3 | 3 to 5 neighbours 
4 | 6 to 10 neighbours 
5 | 11 to 20 neighbours 
6 | More than 20 neighbours 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 

### **Variable label**:   Contact frequency with neighbours        
**Variable name**:   soc_sn_freq_neighbours_0    
**Variable description**:  Indicator of the contact frequency with neighbours that the participant knows well enough to be in touch with or visit with.   
**Value type**:  integer  
**Variable unit**:     
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with neighbours
2 | Weekly contact with neighbours
3 | Biweekly contact with neighbours
4 | Monthly contact with neighbours
5 | Never or less than a year contact with neighbours  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**:   Contact frequency with neighbours        
**Variable name**:   soc_sn_freq_neighbours_1    
**Variable description**:  Indicator of the contact frequency with neighbours that the participant knows well enough to be in touch with or visit with.   
**Value type**:  integer  
**Variable unit**:     
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with neighbours
2 | Weekly contact with neighbours
3 | Biweekly contact with neighbours
4 | Monthly contact with neighbours
5 | Never or less than a year contact with neighbours  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with neighbours        
**Variable name**:   soc_sn_freq_neighbours_2    
**Variable description**:  Indicator of the contact frequency with neighbours that the participant knows well enough to be in touch with or visit with.   
**Value type**:  integer  
**Variable unit**:     
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with neighbours
2 | Weekly contact with neighbours
3 | Biweekly contact with neighbours
4 | Monthly contact with neighbours
5 | Never or less than a year contact with neighbours   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with neighbours        
**Variable name**:   soc_sn_freq_neighbours_3    
**Variable description**:  Indicator of the contact frequency with neighbours that the participant knows well enough to be in touch with or visit with.   
**Value type**:  integer  
**Variable unit**:     
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with neighbours
2 | Weekly contact with neighbours
3 | Biweekly contact with neighbours
4 | Monthly contact with neighbours
5 | Never or less than a year contact with neighbours    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with neighbours        
**Variable name**:   soc_sn_freq_neighbours_4    
**Variable description**:  Indicator of the contact frequency with neighbours that the participant knows well enough to be in touch with or visit with.   
**Value type**:  integer  
**Variable unit**:     
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with neighbours
2 | Weekly contact with neighbours
3 | Biweekly contact with neighbours
4 | Monthly contact with neighbours
5 | Never or less than a year contact with neighbours    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with neighbours        
**Variable name**:   soc_sn_freq_neighbours_5    
**Variable description**:  Indicator of the contact frequency with neighbours that the participant knows well enough to be in touch with or visit with.   
**Value type**:  integer  
**Variable unit**:     
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with neighbours
2 | Weekly contact with neighbours
3 | Biweekly contact with neighbours
4 | Monthly contact with neighbours
5 | Never or less than a year contact with neighbours    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with neighbours        
**Variable name**:   soc_sn_freq_neighbours_6      
**Variable description**:  Indicator of the contact frequency with neighbours that the participant knows well enough to be in touch with or visit with.   
**Value type**:  integer  
**Variable unit**:     
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with neighbours
2 | Weekly contact with neighbours
3 | Biweekly contact with neighbours
4 | Monthly contact with neighbours
5 | Never or less than a year contact with neighbours   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of relatives      
**Variable name**:   soc_sn_num_relatives_0    
**Variable description**:  Indicator of the number of relatives, including siblings and excluding partner/children living at home, which participant is close to, i.e. is in touch with regularly.           
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of relatives      
**Variable name**:   soc_sn_num_relatives_1    
**Variable description**:  Indicator of the number of relatives, including siblings and excluding partner/children living at home, which participant is close to, i.e. is in touch with regularly.           
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of relatives      
**Variable name**:   soc_sn_num_relatives_2    
**Variable description**:  Indicator of the number of relatives, including siblings and excluding partner/children living at home, which participant is close to, i.e. is in touch with regularly.           
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of relatives      
**Variable name**:   soc_sn_num_relatives_3    
**Variable description**:  Indicator of the number of relatives, including siblings and excluding partner/children living at home, which participant is close to, i.e. is in touch with regularly.           
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of relatives      
**Variable name**:   soc_sn_num_relatives_4    
**Variable description**:  Indicator of the number of relatives, including siblings and excluding partner/children living at home, which participant is close to, i.e. is in touch with regularly.           
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of relatives      
**Variable name**:   soc_sn_num_relatives_5    
**Variable description**:  Indicator of the number of relatives, including siblings and excluding partner/children living at home, which participant is close to, i.e. is in touch with regularly.           
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of relatives      
**Variable name**:   soc_sn_num_relatives_6    
**Variable description**:  Indicator of the number of relatives, including siblings and excluding partner/children living at home, which participant is close to, i.e. is in touch with regularly.           
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with family   
**Variable name**:   soc_sn_freq_fam_0    
**Variable description**:  Indicator of the contact frequency with relatives including siblings and children, which participant is close to. This is a different variable from soc_sn_freq_fam_broad, this variable excludes CLSA since CLSA does not specify that these are persons that participant feels close to.               
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with close family
2 | Biweekly contact with close family
3 | Monthly contact with close family
4 | Never or less than a year contact with close family   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with family     
**Variable name**:   soc_sn_freq_fam_1    
**Variable description**:  Indicator of the contact frequency with relatives including siblings and children, which participant is close to. This is a different variable from soc_sn_freq_fam_broad, this variable excludes CLSA since CLSA does not specify that these are persons that participant feels close to.               
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with close family
2 | Biweekly contact with close family
3 | Monthly contact with close family
4 | Never or less than a year contact with close family    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with family    
**Variable name**:   soc_sn_freq_fam_2    
**Variable description**:  Indicator of the contact frequency with relatives including siblings and children, which participant is close to. This is a different variable from soc_sn_freq_fam_broad, this variable excludes CLSA since CLSA does not specify that these are persons that participant feels close to.               
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with close family
2 | Biweekly contact with close family
3 | Monthly contact with close family
4 | Never or less than a year contact with close family       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with family    
**Variable name**:   soc_sn_freq_fam_3      
**Variable description**:  Indicator of the contact frequency with relatives including siblings and children, which participant is close to. This is a different variable from soc_sn_freq_fam_broad, this variable excludes CLSA since CLSA does not specify that these are persons that participant feels close to.               
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with close family
2 | Biweekly contact with close family
3 | Monthly contact with close family
4 | Never or less than a year contact with close family     

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with family   
**Variable name**:   soc_sn_freq_fam_4      
**Variable description**:  Indicator of the contact frequency with relatives including siblings and children, which participant is close to. This is a different variable from soc_sn_freq_fam_broad, this variable excludes CLSA since CLSA does not specify that these are persons that participant feels close to.               
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with close family
2 | Biweekly contact with close family
3 | Monthly contact with close family
4 | Never or less than a year contact with close family      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with family    
**Variable name**:   soc_sn_freq_fam_5      
**Variable description**:  Indicator of the contact frequency with relatives including siblings and children, which participant is close to. This is a different variable from soc_sn_freq_fam_broad, this variable excludes CLSA since CLSA does not specify that these are persons that participant feels close to.               
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with close family
2 | Biweekly contact with close family
3 | Monthly contact with close family
4 | Never or less than a year contact with close family      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with family    
**Variable name**:   soc_sn_freq_fam_6      
**Variable description**:  Indicator of the contact frequency with relatives including siblings and children, which participant is close to. This is a different variable from soc_sn_freq_fam_broad, this variable excludes CLSA since CLSA does not specify that these are persons that participant feels close to.               
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with close family
2 | Biweekly contact with close family
3 | Monthly contact with close family
4 | Never or less than a year contact with close family    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Contact frequency with relatives   
**Variable name**:   soc_sn_freq_relatives_0        
**Variable description**:  Indicator of the contact frequency with relatives, including siblings and children. Note: this is a different variable from soc_sn_freq_fam. This variable includes any relative regardless of how close the participant feels to them.                
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with relatives 
2 | Biweekly contact with relatives 
3 | Monthly contact with relatives 
4 | Never or less than a year contact with relatives  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with relatives      
**Variable name**:   soc_sn_freq_relatives_1          
**Variable description**:  Indicator of the contact frequency with relatives, including siblings and children. Note: this is a different variable from soc_sn_freq_fam. This variable includes any relative regardless of how close the participant feels to them.                
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with relatives 
2 | Biweekly contact with relatives 
3 | Monthly contact with relatives 
4 | Never or less than a year contact with relatives  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with relatives     
**Variable name**:   soc_sn_freq_relatives_2          
**Variable description**:  Indicator of the contact frequency with relatives, including siblings and children. Note: this is a different variable from soc_sn_freq_fam. This variable includes any relative regardless of how close the participant feels to them.                
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with relatives 
2 | Biweekly contact with relatives 
3 | Monthly contact with relatives 
4 | Never or less than a year contact with relatives  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with relatives    
**Variable name**:   soc_sn_freq_relatives_3          
**Variable description**:  Indicator of the contact frequency with relatives, including siblings and children. Note: this is a different variable from soc_sn_freq_fam. This variable includes any relative regardless of how close the participant feels to them.                
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with relatives 
2 | Biweekly contact with relatives 
3 | Monthly contact with relatives 
4 | Never or less than a year contact with relatives    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with relatives    
**Variable name**:   soc_sn_freq_relatives_4          
**Variable description**:  Indicator of the contact frequency with relatives, including siblings and children. Note: this is a different variable from soc_sn_freq_fam. This variable includes any relative regardless of how close the participant feels to them.                
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with relatives 
2 | Biweekly contact with relatives 
3 | Monthly contact with relatives 
4 | Never or less than a year contact with relatives  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with relatives     
**Variable name**:   soc_sn_freq_relatives_5          
**Variable description**:  Indicator of the contact frequency with relatives, including siblings and children. Note: this is a different variable from soc_sn_freq_fam. This variable includes any relative regardless of how close the participant feels to them.                
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with relatives 
2 | Biweekly contact with relatives 
3 | Monthly contact with relatives 
4 | Never or less than a year contact with relatives  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with relatives    
**Variable name**:   soc_sn_freq_relatives_6          
**Variable description**:  Indicator of the contact frequency with relatives, including siblings and children. Note: this is a different variable from soc_sn_freq_fam. This variable includes any relative regardless of how close the participant feels to them.                
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily or weekly contact with relatives 
2 | Biweekly contact with relatives 
3 | Monthly contact with relatives 
4 | Never or less than a year contact with relatives  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of non-kin      
**Variable name**:   soc_sn_num_nonkin_0    
**Variable description**:  Indicator of the number of non-kin members of the participant’s social network consisting of neighbours, colleagues (from work or school), members of associations (that participant is a part of, such as community activities and organization) and friends.         
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of non-kin      
**Variable name**:   soc_sn_num_nonkin_1      
**Variable description**:  Indicator of the number of non-kin members of the participant’s social network consisting of neighbours, colleagues (from work or school), members of associations (that participant is a part of, such as community activities and organization) and friends.         
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of non-kin      
**Variable name**:   soc_sn_num_nonkin_2      
**Variable description**:  Indicator of the number of non-kin members of the participant’s social network consisting of neighbours, colleagues (from work or school), members of associations (that participant is a part of, such as community activities and organization) and friends.         
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of non-kin      
**Variable name**:   soc_sn_num_nonkin_3      
**Variable description**:  Indicator of the number of non-kin members of the participant’s social network consisting of neighbours, colleagues (from work or school), members of associations (that participant is a part of, such as community activities and organization) and friends.         
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of non-kin      
**Variable name**:   soc_sn_num_nonkin_4      
**Variable description**:  Indicator of the number of non-kin members of the participant’s social network consisting of neighbours, colleagues (from work or school), members of associations (that participant is a part of, such as community activities and organization) and friends.         
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of non-kin      
**Variable name**:   soc_sn_num_nonkin_5      
**Variable description**:  Indicator of the number of non-kin members of the participant’s social network consisting of neighbours, colleagues (from work or school), members of associations (that participant is a part of, such as community activities and organization) and friends.         
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Network size of non-kin      
**Variable name**:   soc_sn_num_nonkin_6      
**Variable description**:  Indicator of the number of non-kin members of the participant’s social network consisting of neighbours, colleagues (from work or school), members of associations (that participant is a part of, such as community activities and organization) and friends.         
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Contact frequency with non-kin  
**Variable name**:   soc_sn_freq_nonkin_0          
**Variable description**:  Indicator of the contact frequency with non-kin members of social network, consisting of neighbours, relatives and friends.            
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with non-kin
2 | Weekly contact with non-kin
3 | Biweekly contact with non-kin
4 | Monthly contact with non-kin
5 | Never or less than a year contact with non-kin   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with non-kin  
**Variable name**:   soc_sn_freq_nonkin_1            
**Variable description**:  Indicator of the contact frequency with non-kin members of social network, consisting of neighbours, relatives and friends.            
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with non-kin
2 | Weekly contact with non-kin
3 | Biweekly contact with non-kin
4 | Monthly contact with non-kin
5 | Never or less than a year contact with non-kin  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with non-kin  
**Variable name**:   soc_sn_freq_nonkin_2            
**Variable description**:  Indicator of the contact frequency with non-kin members of social network, consisting of neighbours, relatives and friends.            
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with non-kin
2 | Weekly contact with non-kin
3 | Biweekly contact with non-kin
4 | Monthly contact with non-kin
5 | Never or less than a year contact with non-kin    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with non-kin  
**Variable name**:   soc_sn_freq_nonkin_3            
**Variable description**:  Indicator of the contact frequency with non-kin members of social network, consisting of neighbours, relatives and friends.            
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with non-kin
2 | Weekly contact with non-kin
3 | Biweekly contact with non-kin
4 | Monthly contact with non-kin
5 | Never or less than a year contact with non-kin  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with non-kin  
**Variable name**:   soc_sn_freq_nonkin_4            
**Variable description**:  Indicator of the contact frequency with non-kin members of social network, consisting of neighbours, relatives and friends.            
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with non-kin
2 | Weekly contact with non-kin
3 | Biweekly contact with non-kin
4 | Monthly contact with non-kin
5 | Never or less than a year contact with non-kin  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with non-kin  
**Variable name**:   soc_sn_freq_nonkin_5          
**Variable description**:  Indicator of the contact frequency with non-kin members of social network, consisting of neighbours, relatives and friends.            
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with non-kin
2 | Weekly contact with non-kin
3 | Biweekly contact with non-kin
4 | Monthly contact with non-kin
5 | Never or less than a year contact with non-kin  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:   Contact frequency with non-kin  
**Variable name**:   soc_sn_freq_nonkin_6          
**Variable description**:  Indicator of the contact frequency with non-kin members of social network, consisting of neighbours, relatives and friends.            
**Value type**:  integer  
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
1 | Daily contact with non-kin
2 | Weekly contact with non-kin
3 | Biweekly contact with non-kin
4 | Monthly contact with non-kin
5 | Never or less than a year contact with non-kin  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
# Social support subdomain

### **Variable label**: Received emotional support    
**Variable name**:   soc_ss_rec_emo_0 
**Variable description**:  Frequency of received instrumental support from top 3 network members which are important to the respondent and with whom respondent shared personal experiences and feelings or received affection from.  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never
1 |   Sometimes
2 |   Often

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Perceived social support    
**Variable name**:   soc_ss_perceived_0    
**Variable description**:  respondant feels they have received support from   
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Emotional support      
**Variable name**:   soc_ss_emotional_0    
**Variable description**:  respondant received emotional support:     
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Instrumental support      
**Variable name**:   soc_ss_instrumental_0        
**Variable description**:  respondant feels they have received instrumental support:   
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Social participation subdomain

### **Variable label**:  Social isolation    
**Variable name**:  soc_sp_isolation_0  
**Variable description**:  Indicator of whether participant is socially isolated i.e. no members in social network and no participation in an association (any type, including religious organization).       
**Value type**:  integer  
**Variable unit**:    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not socially isolated, has social network and/ or social participation 
1 |   Socially isolated, no social network and no social participation 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Social isolation    
**Variable name**:  soc_sp_isolation_1  
**Variable description**:  Indicator of whether participant is socially isolated i.e. no members in social network and no participation in an association (any type, including religious organization).       
**Value type**:  integer  
**Variable unit**:    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not socially isolated, has social network and/ or social participation 
1 |   Socially isolated, no social network and no social participation 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
## **Variable label**:  Social isolation    
**Variable name**:  soc_sp_isolation_2  
**Variable description**:  Indicator of whether participant is socially isolated i.e. no members in social network and no participation in an association (any type, including religious organization).       
**Value type**:  integer  
**Variable unit**:    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not socially isolated, has social network and/ or social participation 
1 |   Socially isolated, no social network and no social participation 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
## **Variable label**:  Social isolation    
**Variable name**:  soc_sp_isolation_3  
**Variable description**:  Indicator of whether participant is socially isolated i.e. no members in social network and no participation in an association (any type, including religious organization).       
**Value type**:  integer  
**Variable unit**:    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not socially isolated, has social network and/ or social participation 
1 |   Socially isolated, no social network and no social participation 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
## **Variable label**:  Social isolation    
**Variable name**:  soc_sp_isolation_4  
**Variable description**:  Indicator of whether participant is socially isolated i.e. no members in social network and no participation in an association (any type, including religious organization).       
**Value type**:  integer  
**Variable unit**:    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not socially isolated, has social network and/ or social participation 
1 |   Socially isolated, no social network and no social participation 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
## **Variable label**:  Social isolation    
**Variable name**:  soc_sp_isolation_5  
**Variable description**:  Indicator of whether participant is socially isolated i.e. no members in social network and no participation in an association (any type, including religious organization).       
**Value type**:  integer  
**Variable unit**:    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not socially isolated, has social network and/ or social participation 
1 |   Socially isolated, no social network and no social participation 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
## **Variable label**:  Social isolation    
**Variable name**:  soc_sp_isolation_6  
**Variable description**:  Indicator of whether participant is socially isolated i.e. no members in social network and no participation in an association (any type, including religious organization).       
**Value type**:  integer  
**Variable unit**:    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not socially isolated, has social network and/ or social participation 
1 |   Socially isolated, no social network and no social participation 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
## **Variable label**:  Social isolation    
**Variable name**:  soc_sp_isolation_7  
**Variable description**:  Indicator of whether participant is socially isolated i.e. no members in social network and no participation in an association (any type, including religious organization).       
**Value type**:  integer  
**Variable unit**:    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not socially isolated, has social network and/ or social participation 
1 |   Socially isolated, no social network and no social participation 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Major life events subdomain

### **Variable label**:  Life event: victim     
**Variable name**:  soc_le_vic_0         
**Variable description**:  Respondent was the victim of a crime (i.e. theft, assault) in the past few years.    
**Value type**:  integer    
**Variable unit**: **: N/A      
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Not a victim
1 |  Victim

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: victim     
**Variable name**:  soc_le_vic_1           
**Variable description**:  Respondent was the victim of a crime (i.e. theft, assault) in the past few years.    
**Value type**:  integer    
**Variable unit**: **: N/A      
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Not a victim
1 |  Victim

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: victim     
**Variable name**:  soc_le_vic_2           
**Variable description**:  Respondent was the victim of a crime (i.e. theft, assault) in the past few years.    
**Value type**:  integer    
**Variable unit**: **: N/A      
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Not a victim
1 |  Victim

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: victim     
**Variable name**:  soc_le_vic_3           
**Variable description**:  Respondent was the victim of a crime (i.e. theft, assault) in the past few years.    
**Value type**:  integer    
**Variable unit**: **: N/A      
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Not a victim
1 |  Victim

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: victim     
**Variable name**:  soc_le_vic_4           
**Variable description**:  Respondent was the victim of a crime (i.e. theft, assault) in the past few years.    
**Value type**:  integer    
**Variable unit**: **: N/A      
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Not a victim
1 |  Victim

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: victim     
**Variable name**:  soc_le_vic_5           
**Variable description**:  Respondent was the victim of a crime (i.e. theft, assault) in the past few years.    
**Value type**:  integer    
**Variable unit**: **: N/A      
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Not a victim
1 |  Victim

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: victim     
**Variable name**:  soc_le_vic_6           
**Variable description**:  Respondent was the victim of a crime (i.e. theft, assault) in the past few years.    
**Value type**:  integer    
**Variable unit**: **: N/A      
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Not a victim
1 |  Victim

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: financial problems      
**Variable name**:  soc_le_finance_prob_0             
**Variable description**:  Respondent experienced financial problems in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No financial problems
1 |  Financial problems 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: financial problems      
**Variable name**:  soc_le_finance_prob_1             
**Variable description**:  Respondent experienced financial problems in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No financial problems
1 |  Financial problems 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: financial problems      
**Variable name**:  soc_le_finance_prob_2             
**Variable description**:  Respondent experienced financial problems in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No financial problems
1 |  Financial problems 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: financial problems      
**Variable name**:  soc_le_finance_prob_3               
**Variable description**:  Respondent experienced financial problems in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No financial problems
1 |  Financial problems 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: financial problems      
**Variable name**:  soc_le_finance_prob_4             
**Variable description**:  Respondent experienced financial problems in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No financial problems
1 |  Financial problems 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: financial problems      
**Variable name**:  soc_le_finance_prob_5               
**Variable description**:  Respondent experienced financial problems in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No financial problems
1 |  Financial problems 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: financial problems      
**Variable name**:  soc_le_finance_prob_6               
**Variable description**:  Respondent experienced financial problems in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No financial problems
1 |  Financial problems 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: relationship problems          
**Variable name**:  soc_le_relation_prob_0                        
**Variable description**:  Respondent experienced relationship problems in the past few years.         
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No relationship problems
1 |  Relationship problems

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: relationship problems          
**Variable name**:  soc_le_relation_prob_1                        
**Variable description**:  Respondent experienced relationship problems in the past few years.         
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No relationship problems
1 |  Relationship problems

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: relationship problems          
**Variable name**:  soc_le_relation_prob_2                        
**Variable description**:  Respondent experienced relationship problems in the past few years.         
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No relationship problems
1 |  Relationship problems

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: relationship problems          
**Variable name**:  soc_le_relation_prob_3                        
**Variable description**:  Respondent experienced relationship problems in the past few years.         
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No relationship problems
1 |  Relationship problems

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: relationship problems          
**Variable name**:  soc_le_relation_prob_4                        
**Variable description**:  Respondent experienced relationship problems in the past few years.         
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No relationship problems
1 |  Relationship problems

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: relationship problems          
**Variable name**:  soc_le_relation_prob_5                        
**Variable description**:  Respondent experienced relationship problems in the past few years.         
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No relationship problems
1 |  Relationship problems

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: relationship problems          
**Variable name**:  soc_le_relation_prob_6                        
**Variable description**:  Respondent experienced relationship problems in the past few years.         
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No relationship problems
1 |  Relationship problems

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: illness of family member          
**Variable name**:  soc_le_ill_fam_0                                  
**Variable description**:  Respondent indicated that the illness of family member (partner or other member) occurred in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No illness of family member 
1 |  Illness of family member 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: illness of family member          
**Variable name**:  soc_le_ill_fam_1                                  
**Variable description**:  Respondent indicated that the illness of family member (partner or other member) occurred in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No illness of family member 
1 |  Illness of family member 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: illness of family member          
**Variable name**:  soc_le_ill_fam_2                                  
**Variable description**:  Respondent indicated that the illness of family member (partner or other member) occurred in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No illness of family member 
1 |  Illness of family member 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: illness of family member          
**Variable name**:  soc_le_ill_fam_3                                  
**Variable description**:  Respondent indicated that the illness of family member (partner or other member) occurred in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No illness of family member 
1 |  Illness of family member 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: illness of family member          
**Variable name**:  soc_le_ill_fam_4                                  
**Variable description**:  Respondent indicated that the illness of family member (partner or other member) occurred in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No illness of family member 
1 |  Illness of family member 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: illness of family member          
**Variable name**:  soc_le_ill_fam_5                                  
**Variable description**:  Respondent indicated that the illness of family member (partner or other member) occurred in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No illness of family member 
1 |  Illness of family member 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: illness of family member          
**Variable name**:  soc_le_ill_fam_6                                  
**Variable description**:  Respondent indicated that the illness of family member (partner or other member) occurred in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No illness of family member 
1 |  Illness of family member 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: death of partner            
**Variable name**:  soc_le_death_part_0                                                        
**Variable description**:  Respondent’s partner/ spouse died in the past few years.           
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Partner did not die 
1 |  Partner died 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: death of partner            
**Variable name**:  soc_le_death_part_1                                                        
**Variable description**:  Respondent’s partner/ spouse died in the past few years.           
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Partner did not die 
1 |  Partner died 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: death of partner            
**Variable name**:  soc_le_death_part_2                                                        
**Variable description**:  Respondent’s partner/ spouse died in the past few years.           
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Partner did not die 
1 |  Partner died 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Life event: death of family member or friend           
**Variable name**:  soc_le_death_close_0                                                        
**Variable description**:  Respondent’s child or relative or friend died  in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No death of child/relative /friend
1 |  Death of child/relative /friend

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
## **Variable label**:  Life event: death of family member or friend           
**Variable name**:  soc_le_death_close_1                                                        
**Variable description**:  Respondent’s child or relative or friend died  in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No death of child/relative /friend
1 |  Death of child/relative /friend

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
## **Variable label**:  Life event: death of family member or friend           
**Variable name**:  soc_le_death_close_2                                                        
**Variable description**:  Respondent’s child or relative or friend died  in the past few years.        
**Value type**:  integer      
**Variable unit**: **: N/A        
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  No death of child/relative /friend
1 |  Death of child/relative /friend

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
# Residential characteristics subdomain

### **Variable label**:  Residential stability   
**Variable name**:  soc_resstab_home_0  
**Variable description**:  Number of years living at current home/address  
**Value type**:  integer  
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Residential stability   
**Variable name**:  soc_resstab_comm_0  
**Variable description**:  Number of years living in current neighbourhood  
**Value type**:  integer  
**Variable unit**:    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Home ownership  
**Variable name**:  soc_home_0    
**Variable description**:  Respondent owns the home that they live in   
**Value type**:  integer  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   yes 
0 |   no

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```




