---
title: "Social factors DataSchema"
output: html_document
---

# Table of Contents  
1. [Social network subdomain](#social-inclusion-subdomain)  
2. [Social and community support subdomain](#social-and-community-support-subdomain)  
3. [Social participation subdomain](#social-participation-subdomain)  
4. [Major life events subdomain](#major-life-events-subdomain)  
5. [Home ownership subdomain](#home-ownership-subdomain)

# Social network subdomain

### **Variable label**:   Social network comprehensive 
**Variable name**:   soc_sn_comp_0  
**Variable description**:  Number of social contacts of participant including household members (adults and children), relatives, neighbours, colleagues, members of associations and friends      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  N/A  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Social network small  
**Variable name**:   soc_sn_small_0  
**Variable description**:  Social network comprised of family members, relatives and friends    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  N/A  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Social network small  
**Variable name**:   soc_sn_small_1  
**Variable description**:  Social network comprised of family members, relatives and friends    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  N/A  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Social network friends   
**Variable name**:   soc_sn_friends_0  
**Variable description**:  Social network comprised of friends (living in?)    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  N/A  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Social network friends   
**Variable name**:   soc_sn_friends_1  
**Variable description**:  Social network comprised of friends (living in?)    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  N/A  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**:   Social network relatives   
**Variable name**:   soc_sn_relatives_0  
**Variable description**:  Social network comprised of relatives (living in?)   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  N/A  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 

### **Variable label**:   Social network neighbours   
**Variable name**:   soc_sn_neighbours_0  
**Variable description**:  Social network comprised of neighbours  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  N/A  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 

### **Variable label**:   Social network neighbours   
**Variable name**:   soc_sn_neighbours_1  
**Variable description**:  Social network comprised of neighbours   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  N/A  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 

# Social and community support subdomain

### **Variable label**:   
**Variable name**:   
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Social participation subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Social inclusion subdomain

### **Variable label**:  Social isolation  
**Variable name**:  soc_si_0
**Variable description**:  Respondent has no social contact with anyone (family, relatives, neighbours, friends, colleagues) and no membership in any association  
**Value type**:  integer
**Variable unit**:  N/A
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   yes
1 |   no

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Major life events subdomain

### **Variable label**:  Residential stability 
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Home ownership subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```




